%*******************************************************
% Publications
%*******************************************************
\pdfbookmark[1]{Publications}{publications}
\chapter*{Publications}%\graffito{This is just an early --~and currently ugly~--
% test!}
\label{sec:publications}

The work developed in this thesis led to the following publications:

%\noindent Put your publications from the thesis here. The packages
% \texttt{multibib} or \texttt{bibtopic} etc. can be used to handle multiple different bibliographies in your document.

% \begin{refsection}[ownpubs]
%     \small
%     \nocite{*} % is local to to the enclosing refsection
%     \printbibliography[heading=none]
% \end{refsection}
% 
% \emph{Attention}: This requires a separate run of \texttt{bibtex} for your \texttt{refsection}, \eg, \texttt{ClassicThesis1-blx} for this file. You might also use \texttt{biber} as the backend for \texttt{biblatex}. See also \url{http://tex.stackexchange.com/questions/128196/problem-with-refsection}.


% \bibliographystyleJDHV{alpha}
% \bibliographyJDHV{0_frontmatter/PhDThesis.bib}

\section*{JOURNAL ARTICLES}

\begin{itemize}
  \item[] [JFR'17] \textbf{J. D. Hern\'andez}, E. Vidal, K. Isteni\v{c}, M.
  Moll, M. Carreras, and L. E. Kavraki, ``Online Path Planning for Unexplored
  Underwater Environments using AUVs that Operate under Motion Constraints,''
  Journal of Field Robotics, (in preparation) 2017.
  \item[] [SENSORS'16] \textbf{J. D. Hern\'andez}, K. Isteni\v{c}, N. Gracias,
  N.Palomeras, R. Campos, E. Vidal, R. Garc\'ia, and M. Carreras, ``Autonomous
  Underwater Navigation and Optical Mapping in Unknown Natural Environments,''
  Sensors, vol. 16, no. 8, p. 1174. July 2016.
\end{itemize}

\section*{PEER-REVIEWED CONFERENCES AND WORKSHOPS}

\begin{itemize}
  \item[] [IROS'16] \textbf{J. D. Hern\'andez}, M. Moll, E. Vidal, M. Carreras
  and L. E. Kavraki, ``Planning Feasible and Safe Paths Online for Autonomous
  Underwater Vehicles in Unknown Environments,'' IEEE/RSJ International
  Conference on Intelligent Robots and Systems (IROS), (Daejeon, Korea), pp.
  1313–1320. October 2016.
  \item[] [ROBOT'15] \textbf{J. D. Hern\'andez}, K. Isteni\v{c}, N. Gracias, R.
  Garc\'ia, P. Ridao, and M. Carreras, ``Autonomous Seabed Inspection for
  Environmental Monitoring,'' ROBOT2015: Second Iberian Robotics Conference,
  (Lisbon, Portugal). Springer International Publishing, pp. 27–39. November
  2015.
  \item[] [ICRA'15] \textbf{J. D. Hern\'andez}, E. Vidal, G. Vallicrosa, E.
  Galceran and M. Carreras, ``Online Path Planning for Autonomous Underwater
  Vehicles in Unknown Environments,'' IEEE International Conference on Robotics
  and Automation (ICRA), (Seattle, USA), pp. 1152-1157. May 2015.
  \item[] [NGCUV'15] \textbf{J. D. Hern\'andez}, G. Vallicrosa, E. Vidal, E.
  Pairet, M. Carreras, and P. Ridao. ``Online 3D Path Planning for
  Close-proximity Surveying with AUVs,'' IFAC Workshop on Navigation, Guidance
  and Control of Underwater Vehicles (NGCUV), Girona. April 2015.
\end{itemize}

\section*{OTHER CONFERENCES AND WORKSHOPS}

\begin{itemize}
  \item[] [OCEANS'17] \textbf{J. D. Hern\'andez}, E. Vidal, J. Greer, R. Piasco,
  P. Jaussaud, M. Carreras, and R. Garc\'ia, ``AUV Online Mission Replanning for
  Gap Filling and Target Inspection,'' MTS/IEEE OCEANS, (Aberdeen, Scotland).
  (to appear, 2017).
  \item[] [AUV'16] M. Carreras, \textbf{J. D. Hern\'andez}, E. Vidal, N.
  Palomeras, and P. Ridao, ``Online Motion Planning for Underwater
  Inspection,'' IEEE/OES Autonomous Underwater Vehicles (AUV), (Tokyo, Japan),
  pp. 336-341. November 2016.
  \item[] [OCEANS'15] \textbf{J. D. Hern\'andez}, E. Vidal, G. Vallicrosa, E.
  Pairet, and M. Carreras. ``Simultaneous Mapping and Planning for Autonomous
  Underwater Vehicles in Unknown Environments,'' IEEE OCEANS, (Genova,
  Italy). May 2015.
\end{itemize}

\section*{CONTRIBUTIONS TO OTHER WORKS}

\begin{itemize}
  \item[] [RA-LETTERS'17] E. Vidal, \textbf{J. D. Hern\'andez}, K. Isteni\v{c},
  and M. Carreras, ``Online View Planning for Inspecting Unexplored Underwater
  Structures,'' IEEE Robotics and Automation Letters, vol. 2, no. 3, p. 1436 -
  1443. February 2017.
  \item[] [ICRA'18] E. Pairet, \textbf{J. D. Hern\'andez}, M. Lahijanian, and M.
  Carreras, ``Uncertainty-based Online Mapping and Motion Planning for Marine
  Robotics Guidance,'' IEEE International Conference on Robotics and Automation
  (ICRA), (in preparation) 2018.
\end{itemize}